Meta-analysis Manuscript Wrangling

### 2021-06-30 shared analysis files /manuscript_datavis_22jun21.Rmd
data wrangling file
model wrangling for meeting with sam and mary

---
title: "manuscript_data_wrangling"
author: "Maggie Slein"
date: "6/14/2021"
output: pdf_document
---

@@

#load data
dat_acclim_0<- read_csv("acclimation_full_2june21.csv")
dat_full_var_0 <- read_csv("metafor.csv")
```

@@

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_full_var_ES<-dat_full_var_ES %>% 
  filter (!is.na(yi)) 
```

@@

```{r}
simple_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_acclimation_model
```

```{r}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

# Neglecting Acclimation

This uses the full dataset from my thesis (with more data from the additional search). Interesting that this time, mean temp is the only significant predictor?

```{r}
simple_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_full_var_model
```

```{r}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

```{r}
dat_acclim_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_reared, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("acclimation")
```

```{r}
dat_full_var_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_constant, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("neglecting acclimation (full dataset)")
```

>>>>

---
title: "Meta-analysis Manuscript Wrangling"
author: "Maggie Slein"
date: "6/14/2021"
output: pdf_document
---

@@

#load data
dat_acclim_0<- read_csv("acclimation_dummytherm_30jun.csv")
dat_full_var_0 <- read_csv("metafor.csv")
```

@@

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_full_var_ES<-dat_full_var_ES %>% 
  filter (!is.na(yi)) 
```
# Motivation and Hypotheses

Variability has been identified as important to organismal success and ecosystem dynamics (Vasseur et al 2014). To further understand the impacts of variability of performance, we conducted to analyses on data that explicitly accounted for acclimation (Acclimation model) and studies focuses solely on non-linear averaging (Non-linear averaging model).

H-Acclimation: If reared in fluctuating environments, when exposed to different thermal environments, organisms with larger fluctuation ranges will perform worse than those reared in constant environments. Additional covariates, such as age, size, and expsoure temperature will be correlated negative responses.

H-Non-linear averaging: Organisms will perform better in constant environments than fluctuating environments. Additional covariates, such as age, size, and large fluctuation range will be correlated negative responses.

```{r pressure, echo=FALSE, fig.cap="Conceptual figure demonstrating how acclimation and non-linear averaging account for different aspects of performance.", out.width = '100%'}
knitr::include_graphics("conceptfig_30jun.png")
```

\clearpage

@@

## Acclimation without modifiers
```{r, echo=FALSE, message=FALSE}
simple_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_acclimation_model
```

## Acclimation with modifiers
```{r, echo=FALSE, message=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

# Acclimation data split out by CT data and other thermal performance metrics 
```{r, echo=FALSE, message=FALSE}
CT_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% c("CTmax", "CT max", "CTmin", "LTmax", "LTmin", "Topt", "Tpref", "Thermal preference", "ULT50", "Scope of thermal tolerance (CTmax - CTmin)"))

curve_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% 
           c("CCO activity", "CS activity", "LDH activity", "log CO2 production", 
             "maximal swimming speed", "Maximum burst swim speed", 
             "Performance breadth (Tbr)", "RMR", "ULT50", "Speed", "Time to heat knockdown",
             "Ucrit", "Umax"))
```

## CT aggregated model 
```{r, echo=FALSE, message=FALSE}
CT_model <-rma.mv(yi, vi, data=CT_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
CT_model
```
## Remaining acclimation metrics model 
```{r, echo=FALSE, message=FALSE}
curve_model <- rma.mv(yi, vi, data=curve_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
curve_model
```

# Effects of non-linear averaging
This uses the full dataset from my thesis (with more data from the additional search). Interesting that this time, mean temp is the only significant predictor?

## Non-linear averaging model with no modifiers
```{r, echo= FALSE, message=FALSE}
simple_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_full_var_model
```

## Non-linear averaging model with modifiers
```{r, echo = FALSE, message=FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

# Figures
```{r, echo = FALSE, message=FALSE}
dat_acclim_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_reared, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("Acclimation")
```

```{r, echo = FALSE, message=FALSE}
dat_full_var_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_constant, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("Non-linear averaging")
```
